An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2023-06-05 poly-embed-journal/poly-embed-journal.tex
Updating response and added consistency definiion, proof of Cor 20, top-1, and proofs of theorems 1 and 2

\raf{Restate Thm 1 and give a short proof, either in text since it's SO simple, or formal proof environment}

@@

\raf{Restate theorem 2 and give formal proof (probably two lines) with no additional filler text}

@@

\reviewer{Discussion of polyhedral surrogate for $0-1$ loss}

@@

\raf{TODO: add paragraph on multiclass case, where $k=1$!}

@@

As a finite representative set implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}, Lemma~\ref{lem:X} shows that polyhedral Bayes risks are equivalent to having finite representative sets, which in turn gives an embedding by
Proposition~\ref{prop:representative-embeds-restriction}.
\begin{corollary}\label{cor:poly-risk-fin-rep}
  The following are equivalent for any minimizable loss $L:\R\to\reals^\Y_+$.
  \begin{enumerate}
  \item $\risk{L}$ is polyhedral.
  \item $L$ has a finite representative set.
  \item $L$ embeds a discrete loss.
  \end{enumerate}
\end{corollary}
\begin{proof}
	If $\risk L$ is polyhedral
\end{proof}

@@

@@

\begin{theorem}[Aurenhammer~\cite{aurenhammer1987power}]\label{thm:aurenhammer}
	A cell complex is affinely equivalent to a convex polyhedron if and only if it is a power diagram.
\end{theorem}

>>>>

\reviewer{Restated Thm 1 and gave a short proof}
\embedpolyinformal*
For a proof, observe that Theorem~\ref{thm:discrete-loss-poly-embeddable} proves the first part of the statement, and Theorem~\ref{thm:poly-embeds-discrete} shows the second.

@@

\reviewer{Restated theorem 2 and gave formal proof}
\linkinformal*
\begin{proof}
	By Theorem~\ref{thm:thickened-separated}, we know that if $L$ embeds $\ell$, then there exists an $\epsilon$ such that Construction~\ref{const:eps-thick-link} provides at least one $\epsilon$-separated link $\psi$ with respect to $L$ and $\ell$.
	Moreover, by Theorem~\ref{thm:calibrated-separated}, since $\psi$ is $\epsilon$-separated for $L$ and $\ell$, the pair $(L,\psi)$ is calibrated with respect to $\ell$.
\end{proof}

@@

@@

\reviewer{Paragraph on multiclass case, using top-$k$ with $k=1$}
Observe that while the Weston-Watkins hinge loss was originally designed as a surrogate for $0-1$ loss in multiclass settings, there is no link such that $(L^{WW}, \psi)$ is consistent with respect to $\ell^{0-1}$. 
However, we can construct a polyhedral surrogate and use the canonical argmax link for $\ell^{0-1}$ by simply using the $L^k$ surrogate with $k=1$. 
The $L^k$ surrogate simplifies to 
\begin{align*}
	L^1(u)_y &= \left(\max_m \frac{m-1}{m} + \frac 1 m \sum_{i=1}^m u_{[i]} \right) - u_y~.
\end{align*}
\jessie{Does this simplify further? I don't think so}

@@

\reviewer{Forward ref}
Lemma~\ref{lem:X} now allows us to observe the relationship between embeddings, finite representative sets and polyhedral Bayes risks; we expand on this relationship in Propositions~\ref{prop:embed-bayes-risks} and \ref{prop:embed-iff-trims-equal}.
%As a finite representative set implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}, Lemma~\ref{lem:X} shows that polyhedral Bayes risks are equivalent to having finite representative sets, which in turn gives an embedding by
Proposition~\ref{prop:representative-embeds-restriction}.
\begin{corollary}\label{cor:poly-risk-fin-rep}
  The following are equivalent for any minimizable loss $L:\reals^d\to\reals^\Y_+$.
  \begin{enumerate}
  \item $\risk{L}$ is polyhedral.
  \item $L$ has a finite representative set.
  \item $L$ embeds a discrete loss.
  \end{enumerate}
\end{corollary}
\reviewer{Adding formal proof.}
\begin{proof}
	If $\risk L$ is polyhedral, then Lemma~\ref{lem:X} implies that $L$ has a finite representative set.
	Moreover, if $L$ has a finite representative set $\Sc$, then Proposition~\ref{prop:representative-embeds-restriction} implies that $L$ embeds $L|_{\Sc}$, which is finite.
	Lemma~\ref{lem:loss-restrict} additionally implies that $\risk L = \risk{L|_{\Sc}}$, which is polyhedral as the pointwise supremum of a finite set of affine functions.
\end{proof}

@@

\section{Consistency}\label{app:consistency}
Definitions of consistency tend to vary slightly within the literature; in general, the spirit of consistency definitions boil down to ``approaching the optimal hypothesis in surrogate space implies approaching the optimal hypothesis in the target space'' upon applying the link function.
\citet[Theorem 1]{bartlett2006convexity} shows that ``classification calibration'' is equivalent to this notion of consistency.
The equivalence (when the hypothesis class is the set of all measurable functions) between consistency and calibration is what allows one to abstract away the features $\X$ and simply consider conditional distributions.

For the purposes of this work, we consider the following definition of consistency, which aligns with the literature~\citep{bartlett2006convexity,agarwal2015consistent,ramaswamy2016convex}.

\begin{definition}[Consistency]
	Given a loss $L : \reals^d \to \reals^\Y_+$ and link $\psi : \reals^d \to \R$, the pair $(L, \psi)$ is \emph{consistent} with respect to a target loss $\ell : \R \to \reals^\Y_+$ if, for all $D \in \Delta(X \times \Y)$ and all sequences of measurable functions $\{f_m : \X \to \reals\}$, we have
	\begin{align*}
		\E_{(X,Y) \sim D} L(f_m(X), Y) \to \inf_f  \E_{(X,Y) \sim D} L(f(X), Y) &\implies \E_{(X,Y) \sim D} \ell(\psi \circ f_m(X), Y) \to \inf_f  \E_{(X,Y) \sim D} \ell(\psi \circ f(X), Y)~.
	\end{align*}
\end{definition}

When the hypothesis class $\H$ is not the set of measurable functions, $\H$-calibration and $\H$-consistency are not necessarily equivalent~\citep{long2013consistency,zhang2020bayes}.

@@

\begin{theorem}[Aurenhammer~\citep{aurenhammer1987power}]\label{thm:aurenhammer}
	A cell complex is affinely equivalent to a convex polyhedron if and only if it is a power diagram.
\end{theorem}

### 2023-06-05 poly-embed-journal/reviews/jmlr-response.tex
Updating response and added consistency definiion, proof of Cor 20, top-1, and proofs of theorems 1 and 2

\documentclass[a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{xcolor}

@@

\newcommand{\Comments}{1}
\definecolor{gray}{gray}{0.5}
\definecolor{lightred}{rgb}{1,0.6,0.6}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\ian}[1]{\mynote{blue}{[IK: #1]}}
\newcommand{\iant}[1]{\mytodo{blue!20!white}{IK: #1}}
\newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}

@@

\raf{OLD TEXT}
  We thank the editor and reviewers for their feedback.  While the instructions said only a brief response was needed, we have elected to provide a full letter because we discovered we needed a stronger condition than had actually been assumed.  Essentially, the error was that in the proofs of Lemma 8 and Corollary 7 it was mistakenly assumed that the span of a level set of an identifiable property and the kernel of the identification function for that level set should have the same codimension, when actually the codimension of the former could be unboundedly larger than that of the latter.  A way to avoid this, which we have adopted, is to assume that 0 is in the interior of the image of the identification function, an assumption inspired by Assumption V1 of Fissler and Ziegel (2016) and similar in spirit to our existing conditions.

We first discuss the changes needed to implement this correction, and then address the changes to address other comments, all of which were minor.\\
\\
Regards,\\
Jessica Finocchiaro, Rafael Frongillo, and Bo Waggoner

@@

@@

  We have fixed all minor issues.
  We added the definition of a link function to Definition 6, and emphasized the definition of a calibrated link in Definition 6 as well.
  We added a formal definition of consistency into the appendix with discussion about this definition and its history.\raft{I'm actually wondering if we should just define it in the paper like they suggest... let's see how the appendix section turns out}
  We thank the reviewer for their suggestions to restate Theorems 1 and 2 where relevant; we have done so.

@@

>>>>

\documentclass[a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{xcolor}
\usepackage{hyperref}

@@

\newcommand{\Comments}{1}
\definecolor{gray}{gray}{0.5}
\definecolor{lightred}{rgb}{1,0.6,0.6}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\jessie}[1]{\mynote{blue}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{blue!20!white}{JF: #1}}
\newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}

@@

\raf{OLD TEXT}
  We thank the editor and reviewers for their feedback.

We first discuss the changes needed to implement this correction, and then address the changes to address other comments, all of which were minor.\\
\\
Regards,\\
Jessie Finocchiaro, Rafael Frongillo, and Bo Waggoner

@@

We thank the reviewer for their thoughtful review and careful reading of our work. We have incorporated the editing suggestions made, and marked in our revised manuscript where non-typo changes to the text were made. 
To answer the first bullet, the reviewer is correct that the pair is not calibrated; we have clarified this point in a following sentence. 
To answer their final question, each element of $\mathcal{U}$ is a set, so the union $\cup \mathcal{U}$ is a set of real-valued $v \in \mathbb{R}^d$; hence it is not a typo.

@@

  We have fixed all minor issues.
  We added the definition of a link function to Definition 6, and emphasized the definition of a calibrated link in Definition 6 as well.
  We added a formal definition of consistency into the appendix with discussion about this definition and its history.\raft{I'm actually wondering if we should just define it in the paper like they suggest... let's see how the appendix section turns out} \jessiet{based on first pass of appendix section, might be in favor of adding in to body.}
  We thank the reviewer for their suggestions to restate Theorems 1 and 2 where relevant; we have done so.

@@

We thank the reviewer the feedback. We will discuss the concerns point by point.

\begin{enumerate}
	\item \emph{Is the current framework can be extended to more general class of loss beyond polyhedral?}

	The reviewer is correct that the paper is essentially restricted to the polyhedral setting.  (There are extensions beyond the polyhedral case in Section 6, but not far beyond.)  Our goal is not to characterize the full set of consistent surrogates, but to provide a general framework for the design and analysis of polyhedral surrogate losses.

	\item \emph{Suggestion for empirical validation on multiclass classification}

	We thank the reviewer for the suggestion.  Ultimately, however, we feel that such a toy example would not be very illuminating for our particular results.  For multiclass classification, as in the reviewer’s example, many other papers already cover consistency conditions in theory and practice quite thoroughly, whereas the contribution of our paper is in more complex settings.  Even the comparison among different surrogates for multiclass classification appears in tutorials, blogs, and surveys such as \href{https://faculty.ist.psu.edu/vhonavar/Courses/ds310/lossfunc.pdf}{this}. 
	In lieu of a toy example, we feel that the applications in Section~\ref{sec:applications} illustrate the machinery we develop, leaving the evaluation and demonstration of the resulting surrogates (in the proper contexts) to the follow-up works cited there.

	\item \emph{When should we adopt the polyhedral loss instead of existing well-known convex surrogates such as logistic or hinge loss for a particular task?}

	To clarify, hinge loss is an example of an embedding.  See the previous response and “Polyhedral vs. smooth surrogates” in Section~\ref{sec:conclusion} for discussion on how to select surrogates.

	\item \emph{The claim that ``consistency depends crucially on the choice of link function.''}

	The choice of surrogate loss is of course important for consistency, but so is the choice of link function; see the discussion after Definition~\ref{def:indirect-elic}.  
	(In particular, it seems the reviewer may be fixing the link to be the sign function; e.g. logistic loss is consistent with respect to 0-1 loss when using the sign link, but not with any other link.)
